Approximation as Differentiation notes

### 2025-02-21 notes/definitions.tex
Define commutative monoid.

@@

$\CMon$ is the category whose objects are the commutative monoids $M$ and morphisms $M \to M'$ are the
commutative monoid homomorphisms. $\CMon$ is symmetric closed monoidal, with the trivial one-element monoid
$\One$ as terminal object and monoidal product $M \tensor M'$ given by the direct product of $M$ and $M'$.
$\CMon$ is complete and cocomplete, inheriting all limits and colimits from $\Set$.

>>>>

\subsection{Commutative monoids}

A \emph{commutative monoid} $A = (A, \varepsilon, +)$ is a set equipped with distinguished element
$\varepsilon \in A$ called the \emph{unit} and associative binary operation $+$ satisfying $\varepsilon + x =
x$ and $x + \varepsilon = x$ for any $x \in A$.

@@

$\CMon$ is the category whose objects are the commutative monoids $A$ and morphisms $A \to B$ are the
commutative monoid homomorphisms. $\CMon$ is symmetric closed monoidal, with the trivial one-element monoid
$\One$ as terminal object and monoidal product $A \tensor B$ given by the direct product of $A$ and $B$.
$\CMon$ is complete and cocomplete, inheriting all limits and colimits from $\Set$.

Although $\CMon$ is not Cartesian closed, every hom-object $\CMon(A,B)$ is a commutative monoid, with the
constant homomorphism that sends every element of the carrier of $A$ to $1_A$ as the unit, and pointwise
multiplication as the binary operation.
